Comparison of simulation to theory

### 2016-02-26 sims/compare-to-theory.Rmd
haplotype length comparison works!

matplot(xx, sim_lens, type='l', lty=sapply(chunks.rvals,"[",1),
        main="mean haplotype length",
        xlab="spatial position", ylab="mean B haplotype length (incl. zeros)")
matlines( rev(xgrid$x.mid), hap.len.mat, lty=3 )
legend("topleft", lty=c(sapply(chunks.rvals,"[",1),3), col=c(rep_len(1:6,ncol(sim_cond_lens)),1),
        legend=c( sapply( chunks.rvals, function (x) { sprintf("chr %d: %0.3f",x[1],x[2]) } ), "theory") )
```

@@

```

Here are haplotype probabilities (**not** cumulative):
```{r look_at_haps}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=-haplen/2, right=haplen/2 )
    image(hap.probs, legend=TRUE, yaxt='n', zlim=range(hap.probs[,-1]),
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
    locator(1)
}
```
and here are the same offset by `r rgrid$dx[1]`
```{r look_at_haps_offset}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=rgrid$dx[1], right=rgrid$dx[1]+haplen )
    image(hap.probs, legend=TRUE, yaxt='n', zlim=range(hap.probs[,-1]),
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```

>>>>

matplot(xx, sim_lens, type='l', lty=sapply(chunks.rvals,"[",1),
        main="mean haplotype length", ylim=range(sim_lens,hap.len.mat),
        xlab="spatial position", ylab="mean B haplotype length (incl. zeros)")
matlines( rev(xgrid$x.mid), hap.len.mat, lty=3 )
legend("topleft", lty=c(sapply(chunks.rvals,"[",1),3), col=c(rep_len(1:6,ncol(sim_cond_lens)),1),
        legend=c( sapply( chunks.rvals, function (x) { sprintf("chr %d: %0.3f",x[1],x[2]) } ), "theory") )
```

@@

x.inds <- floor(seq(1,length(xgrid$x.mid),length.out=11))
xx <- xgrid$x.mid[x.inds]
nxab <- attr(hap.pdf,"soln.dims")[1]  # number of space x AB combinations
r.lens <- attr(hap.pdf,"r")[,"right"] - attr(hap.pdf,"r")[,"left"]
lenvals <- seq(0,1,length.out=21)
hap.distrns <- sapply( x.inds, function (xk) {
        kk <- 1 + which( ( (0:(ncol(hap.pdf)-2)) %% nxab )+1 == xk )
        y <- tapply( hap.pdf[nrow(hap.pdf),kk], match(r.lens,sort(unique(r.lens))), sum )
        # not really a density: need to divide
        diff(c(0,approx( sort(unique(r.lens)), cumsum(y), xout=lenvals )$y))
    } )
matplot( lenvals, hap.distrns, type='l', xlab="haplotype length", ylab="probability density" )
legend("topright", lty=1:5, col=1:6, legend=sprintf("location = %0.2f", xx))
```

Here are haplotype probabilities (**not** cumulative):
```{r look_at_haps}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32, 0.64) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=-haplen/2, right=haplen/2 )
    image(hap.probs, legend=TRUE, yaxt='n', zlim=range(hap.probs[,-1]),
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```
and here are the same offset by `r rgrid$dx[1]`
```{r look_at_haps_offset}
for (haplen in c(0.02, 0.04, 0.08, 0.16, 0.32, 0.64) ) {
    hap.probs <- get_hap_probs( hap.pdf, left=rgrid$dx[1], right=rgrid$dx[1]+haplen )
    image(hap.probs, legend=TRUE, yaxt='n', zlim=range(hap.probs[,-1]),
       main=paste(c("A:","B:"),paste(round(attr(hap.probs,"r"),3),collapse=" to ")) )
    axis(2,at=(pretty(xgrid$x.mid)-min(xgrid$x.mid))/diff(range(xgrid$x.mid)),labels=pretty(xgrid$x.mid))
}
```
